Icicle: fuse your queries

### 2016-04-11 2016fhpc/section/XX-Related.tex
ok

>>>>

Continuous queries are a similar domain, where a single query keeps running and producing results, as data is received.
In \cite{munagala2007optimization} there are multiple queries based off the same incoming stream.
Each queries is filtered by a conjunction of predicates, where each single predicate may be used by multiple queries.
If these predicates are expensive to compute, it is certainly not ideal to compute these for each query.
